SDR enhancement by clouds

### 2024-03-17 GHI_enh_04_investigate.tex
Commit 2024-03-16 16:14
Commit 2024-03-16 17:10
Commit 2024-03-17 22:10

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-15}

@@

@@

\begin{verbatim}
2024-03-15 18:54:55.8 athan@tyler GHI_enh_04_investigate.R 1.392723 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-17}

@@

lmY: 0.183685 +/- 0.040872

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P_energy-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy_multi-1} \end{center}

@@

\begin{verbatim}
2024-03-17 20:07:26.4 athan@tyler GHI_enh_04_investigate.R 1.254163 mins
\end{verbatim}

### 2024-03-17 article/article.Rmd
Commit 2024-03-17 22:10

We decided to use the Libradtran [@Emde2016] radiation transfer model, to modeled
the clear sky equivalent of GHI, with monthly climatological data of AOD and water
column from the Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998].  Our site
participates in AERONET, where we operate a Cimel photometer, colocated to
the CM-21 pyranometer, since 2003

@@

```{r echo=FALSE, fig.cap="Treds of the mean over irradiance per CE"}
knitr::include_graphics("../images/energy-3.png")
```

```{r echo=FALSE, fig.cap="Treds of the mean over irradiance per CE"}
knitr::include_graphics("../images/P_energy-3.pdf")
```

>>>>

We decided to use the Libradtran [@Emde2016] radiation transfer model, to modeled
the clear sky equivalent of GHI, with monthly climatological data of AOD and water
column from the Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998].  Our site
participates in AERONET, where we operate a Cimel photometer, collocated to
the CM-21 pyranometer, since 2003

@@

<!-- ```{r echo=FALSE, fig.cap="Treds of the mean over irradiance per CE"} -->
<!-- knitr::include_graphics("../images/energy-3.png") -->
<!-- ``` -->

```{r echo=FALSE, fig.cap="Treds of the mean over irradiance per CE"}
knitr::include_graphics("../images/P_energy-7.png")
```
